Modeling and analyzing the Corona-virus warning app with the Isabelle Infrastructure framework

### 2020-07-11 paper.tex
one <<<HEAD had to be deleted

For the DP-3T Ephemeral Ids \cite{dp3t:wp}, for each day $t$ a seed $SK_t$
is used to generate a list of length $n = 24 * 60 / L$, where $L$ is the duration for which
the Ephemeral Ids are posted by the smart phone
\begin{ttbox}
  EphId1 || ... || EphIdn = PRG(PRF(SKt,``broadcast key''))
\end{ttbox} 
``where PRF is a pseudo-random function (e.g., HMAC-SHA256), ``broadcast key'' is a
fixed, public string, and PRG is a pseudo-random generator (e.g. AES in counter mode)'' \cite{dp3t:wp}
%\TODOref{DP-3T Whitepaper}.

@@

\section{Summary and discussion of relevance of the approach}
%{Conclusions}
\label{sec:concl}
%\subsection{Protection goals of attacks}
%\subsection
We can establish in our formal framework an attack that even a system using changing
Ephemeral ids can be broken if the attacker physically follows a victim. This is a basic attack on
anonymity: a user's connection between his Ephemeral Ids and personal details (Iphone MAC or name)
is revealed to the attacker. The protection goal of privacy is thereby destroyed.

>>>>

For the DP-3T Ephemeral Ids \cite{dp3t:wp}, for each day $t$ a seed $SK_t$
is used to generate a list of length $n = 24 * 60 / L$, where $L$ is the duration for which
the Ephemeral Ids are posted by the smart phone
\begin{ttbox}
  EphId1 || ... || EphIdn = PRG(PRF(SKt,``broadcast key''))
\end{ttbox} 
``where PRF is a pseudo-random function (e.g., HMAC-SHA256), ``broadcast key'' is a
fixed, public string, and PRG is a pseudorandom generator (e.g. AES in counter mode)'' \cite{dp3t:wp}.

@@

\section{Summary and discussion of relevance of the approach}
%{Conclusions}
\label{sec:concl}
%\subsection{Protection goals of attacks}
%\subsection
=======
\subsection{Protection goals of attacks}
Bluetooth based proximity tracing gives rise to a variety of noteworthy privacy and security issues that deserve formal consideration (and verification). The debate emerging between advocates of centralized architectures and those in favor of a decentralized approach in particular yields a lot of interesting material detailing different attacks and possible mitigation strategies: \cite{pepppt:dp3tana}, \cite{pepppt:dp3tresp}, \cite{dp3t:psre}.

In terms of attack scenarios, connecting an Ephemeral Id to a particular device is the first step into multiple different attacks, we want to classify as deanonymisation attacks:
\begin{itemize}
\item \textbf{Tracking a device}
  \cite{dp3t:psre}[p9], \cite{pepppt:dp3tana}[p8]\\
  Bluetooth enabled devices introduce some fundamental risks, that are not
  specific to proximity detection: If the Bluetooth signal is linked to a fixed
  identifier, say a MAC address, constant broadcasting makes
  a device trackable.
  Periodically changing Ephemeral Ids can be an effective mitigation\footnote{%
    In addition Bluetooth has to be configured to use rotating MAC addresses
    instead of fixed ones, as is the default in modern smartphone operating
    systems. Also, rotation of Bluetooth identifiers has to happen
    in sync with MAC address randomization; the Apple/Google proposal
    \cite{enf:bluetooth} ensures this.}
  as they limit the time frame in which a certain id can be used to
  track the corresponding device, hence, rendering the attack not impossible
  but significantly less severe.
\item \textbf{Identify infected individuals}
  \cite{dp3t:psre}[p5], \cite{pepppt:dp3tana}[p9]\\
  Like any notification about, e.\,g., a STD, might inform a spouse about the
  infidelity of the other, given the right circumstances, being notified about a
  possible exposure to COVID-19 might reveal illicit information to
  the recipient like who it was that tested positive for the virus.
  This is an inherent vulnerability of any such system,
  whether it is analogous or digital (digitally aided).\footnote{
    As DP-3T emphasizes, it it, indeed, inherent to proximity tracing in general
    \cite{dp3t:psre}[p6].
    The likelihood of said circumstances to occur, however,
    might increase when notifications are carried out automatically.
    Therefore, we feel that it is, nonetheless, worth considering.}
  In contrast to tracking a Bluetooth enabled device,
  this attack is not considerably mitigated by changing Ephemeral Ids:
  %Once connected to a device or individual, an Ephemeral Id might yield the
  %desired information for up to 14 days
  A positive test result can be reported for as much as 14 days after the
  compromised Ephemeral Id was used and still reveal the desired information.
\end{itemize}

\begin{figure}[htb]
  \begin{center}
    \includegraphics[width=6in]{DP-3T_deanonymisation_attacks}
  \end{center}
  \caption{Two deanynomisation attacks: Tracking users and identifying confirmed COVID-19 cases}
  \label{fig:dp3tprot}
\end{figure}

\subsection{Summary and discussion of relevance of the approach}
We can establish in our formal framework an attack that even a system using changing
Ephemeral ids can be broken if the attacker physically follows a victim. This is a basic attack on
anonymity: a user's connection between his Ephemeral Ids and personal details (Iphone MAC or name)
is revealed to the attacker. The protection goal of privacy is thereby destroyed.
